\input{preamble}

\title{\vspace{-1.5cm}\textbf{Weilight Harbor — Progress Report (Week 11)}\\
       \large COMP3030J Web Development, UCD, 2025/26 — Group 14}
\author{}
\date{}

\begin{document}
\maketitle
\vspace{-2.0cm}
\begin{center}
  \small
  Live deployment: \url{http://csi6220-2-vm3.ucd.ie} \quad
  Repository: \url{https://github.com/licctvcctv/weilight-harbor}
\end{center}
\vspace{0.4cm}

% =====================================================================
\section{Summary}

Weilight Harbor is feature-complete for the Week~11 submission. All five
planned user-facing modules (Community, Crowdfunding, Life Journal,
Respite Station, User Centre) plus the Admin moderation panel are
deployed on the assigned UCD VM and reachable on the public URL above.
Both Mandarin and English locales are supported end-to-end with 511
translated strings. Continuous deployment runs through GitHub Actions: a
push to \texttt{main} triggers a workflow that hops through the UCD jump
host (password + TOTP), force-resets the working tree to the latest
commit, runs \texttt{vm\_update.sh}, and restarts Gunicorn.

This week we are submitting two PDF drafts
(\texttt{14\_system\_draft.pdf}, \texttt{14\_user\_draft.pdf}) on
Moodle and finalising peer-testing materials for Week~12.

% =====================================================================
\section{Completed since Week 10}

\begin{itemize}
  \item Bilingual admin panel (i18n applied to Layui pages).
  \item GitHub Actions deploy workflow with TOTP + jump-host
        \texttt{expect} script.
  \item Pagination fixes on the User Centre history page
        (\texttt{url\_for(...,**\{page\_param: n\})} replacing the brittle
        \texttt{\&} concatenation that survived the early prototype).
  \item Sensitive-word severity tiers (warning vs.\ crisis modal) wired
        through community and confessions.
  \item Seed data refresh: 8 users, 12 community posts, 7 campaigns,
        82 donations, 50 journal entries, 8 respite requests, 15
        confessions.
  \item Documentation: README expansion, this Week~11 progress report,
        and the System / User document drafts.
  \item Deployment hardening:
        \begin{itemize}
          \item Force-checkout to \texttt{main} (the VM had been stuck
                on an empty \texttt{master} branch from the original
                tar-based bootstrap, which is why earlier
                \emph{"successful"} deploys never updated the live
                site).
          \item Auto-seed when the database is empty.
          \item One-shot vendor sync for the gitignored Layui / TinyMCE
                / ECharts assets (\texttt{./deploy.sh --sync-vendor}).
          \item Diagnostics-only mode (\texttt{./deploy.sh --diag}).
          \item SHA-equality assertion after every deploy.
        \end{itemize}
\end{itemize}

% =====================================================================
\section{Plan for Weeks 11–15}

\begin{tabularx}{\linewidth}{@{} L{1.0cm} L{4.0cm} X @{}}
  \toprule
  \textbf{Week} & \textbf{Focus} & \textbf{Deliverables} \\
  \midrule
  11 & System \& User document drafts
     & \texttt{14\_system\_draft.pdf}, \texttt{14\_user\_draft.pdf} on
       Moodle by Friday midnight. \\
  12 & Peer testing
     & Run two test sessions; complete the two feedback forms (user +
       system) for the assigned groups; receive feedback from two
       groups. \\
  13 & Final polish
     & Final system document ($\leq$20 pages), final user document
       ($\leq$10 pages); incorporate peer-testing feedback. \\
  14 & Demo rehearsal
     & Internal dry-run; prepare slides; finalise per-member
       contribution table. \\
  15 & Final demonstration and submission
     & Final demo, final code freeze, archive. \\
  \bottomrule
\end{tabularx}

% =====================================================================
\section{Outstanding work}

\subsection*{Documentation}
\begin{itemize}
  \item Replace placeholder names / percentages in the System Document
        Section~4 (Team Contribution).
  \item Insert real screenshots into the User Document.
  \item Confirm wording of the generative-AI usage section with the
        team.
\end{itemize}

\subsection*{Product polish}
\begin{itemize}
  \item Finish the forgot-password flow (UI exists; SMTP is not
        provisioned on the VM. Decision: leave stubbed for the
        assignment scope.)
  \item Tighten responsive breakpoints on the Respite map list panel.
  \item Seed at least one user with $>10$ entries in a year so the
        Annual Film button is visible to evaluators by default.
\end{itemize}

\subsection*{Peer-testing preparation (Week 12)}
\begin{itemize}
  \item Prepare a one-page \emph{test scenario} sheet with login
        credentials and six user journeys (register, post, donate,
        journal, respite request, admin review).
  \item Confirm the two feedback forms (user + system) are filled in
        for each of the two groups assigned to us.
  \item Reserve the test slot on the shared schedule.
\end{itemize}

% =====================================================================
\section{Risks}

\begin{tabularx}{\linewidth}{@{} L{4.6cm} l l X @{}}
  \toprule
  \textbf{Risk} & \textbf{Likelihood} & \textbf{Impact} & \textbf{Mitigation} \\
  \midrule
  Jump-host TOTP secret rotates before final submission
    & Low & High
    & Fall-back to manual \texttt{bash deploy.sh}; secret stored in
      GitHub Secrets and in the team password manager. \\
  VM disk fills up due to uploads
    & Low & Medium
    & Static uploads bounded by extension allow-list; current usage
      $\approx$40\,\% of 30\,GB. \\
  SQLite write contention during demo
    & Low & Medium
    & Demo audience size is small; if needed switch to a single-worker
      Gunicorn for the demo. \\
  Late-binding peer-testing feedback
    & Medium & Low
    & Allocate Day 1 of Week~13 strictly to feedback ingestion. \\
  \bottomrule
\end{tabularx}

% =====================================================================
\section{Asks for the tutor}

\begin{enumerate}
  \item Confirmation that the Week~11 cover sheet should follow the
        standard module template (no separate group cover required).
  \item Confirmation that simulated donations are acceptable as
        \emph{"transaction"} coverage in the System Document.
  \item Indicative page weighting between \emph{Technical Implementation}
        and \emph{AI Use} sections in the rubric (we have budgeted
        $10$–$12$ vs.\ $1$–$2$).
\end{enumerate}

\vspace{0.6cm}
\noindent
\textit{Prepared by Group~14. The complete System and User drafts
accompany this report under \texttt{docs/}.}

\end{document}
